Causes and effects in Dichotomous Comparative Judgments: an information-theoretical system of plausible mechanism

### 2024-08-01 _tex/index.tex
Built site for gh-pages

\includegraphics[width=0.4\textwidth,height=\textheight]{images/figures/dag_bb1.png}

@@

\includegraphics[width=0.4\textwidth,height=\textheight]{images/figures/dag_bb2.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{images/figures/dag_bb3.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{images/figures/dag_bb4.png}

@@

\includegraphics[width=1\textwidth,height=\textheight]{images/figures/dag_bb5.png}

>>>>

\includegraphics[width=0.3\textwidth,height=\textheight]{images/figures/dag_bb1.png}

@@

\includegraphics[width=0.3\textwidth,height=\textheight]{images/figures/dag_bb2.png}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{images/figures/dag_bb3.png}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{images/figures/dag_bb4.png}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{images/figures/dag_bb5.png}
